cpcrw_ms

### 2015-10-07 manuscript/cpcrw_manuscript.Rmd
Tweaks
Introduction outline
Re issue #14.

Introduction.

Boreal forests, permafrost, importance of active layer.

Moisture likely to be a strong control of C oxidation. Which form? Importance of CO2 / CH4 balance.

@@

@@

>>>>

* Boreal biome and climate change.
 * Climate change and warming boreal biome.
 * Variety of changes occurring - Alaska in particular.
 * Vegetation transitions (setting up for transition zone sampling).

* Potential soils and permafrost C feedback. 
 * Soils hold a lot of C, particularly at high latitudes.
 * Importance of active layer.
 * Uncertainty of climate feedback.

* Moisture likely to be a strong control of C oxidation.
 * Cite theoretical, experimental, modeling work here. 
 * Soil drainage/anoxia is *highly* uncertain.
 * Will determine both magnitude and form (CO2/CH4) of oxidation.
 * This will have different feedback effects.

* Goals of this study.
 * Sample AL soils at maximum AL depth, vegetation transition zone (high enough to warm, still lots of C).
 * Manipulative experiment (drought and temperature) examining CO2/CH4 emissions.
 * Link to structural/biological measurements.

@@

**Laboratory iincubation*

@@

Note open experiment...

**Statistical analysis**
